---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linkET

<!-- badges: start -->
<!-- badges: end -->

The goal of `linkET` is to visualize simply and directly a matrix heatmap based
on 'ggplot2'. **Note: all functions of network have been merged in netET package.**

## Installation

You can install the released version of `linkET` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Hy4m/linkET", force = TRUE)
packageVersion("linkET")
```
## Example

This is a basic example which shows you how to solve a common problem:

### Data processing

```{r data_processing}
library(linkET)
## matrix_data
matrix_data(list(mtcars = mtcars))

## md_tbl
matrix_data(list(mtcars = mtcars)) %>% 
  as_md_tbl()

## as method
as_matrix_data(mtcars)

as_md_tbl(mtcars)

## special function for correlation matrix
correlate(mtcars) %>% 
  as_matrix_data()

correlate(mtcars) %>% 
  as_md_tbl()
```

### Heatmap

```{r heatmap}
library(ggplot2)
matrix_data(list(mtcars = mtcars)) %>% 
  hyplot(aes(fill = mtcars)) +
  geom_tile()

as_md_tbl(mtcars) %>% 
  hyplot(aes(size = mtcars)) +
  geom_point(shape = 21, fill = NA)

correlate(mtcars) %>% 
  as_md_tbl() %>% 
  qcorrplot() +
  geom_square()

library(vegan)
data("varespec")
data("varechem")
correlate(varespec[1:30], varechem) %>% 
  qcorrplot() +
  geom_square() +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(11, "RdBu"))

qcorrplot(varespec[1:30], type = "lower") +
  geom_square() +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(11, "RdBu"))

## you can set your style
set_corrplot_style()
qcorrplot(mtcars) + geom_square()

## reset to default style
set_default_style()
```

## mantel test

```{r mantel}
library(dplyr)
data("varechem", package = "vegan")
data("varespec", package = "vegan")

mantel <- mantel_test(varespec, varechem,
                      spec_select = list(Spec01 = 1:7,
                                         Spec02 = 8:18,
                                         Spec03 = 19:37,
                                         Spec04 = 38:44)) %>% 
  mutate(rd = cut(r, breaks = c(-Inf, 0.2, 0.4, Inf),
                  labels = c("< 0.2", "0.2 - 0.4", ">= 0.4")),
         pd = cut(p, breaks = c(-Inf, 0.01, 0.05, Inf),
                  labels = c("< 0.01", "0.01 - 0.05", ">= 0.05")))

qcorrplot(correlate(varechem), type = "lower", diag = FALSE) +
  geom_square() +
  geom_couple(aes(colour = pd, size = rd), 
              data = mantel, 
              curvature = nice_curvature()) +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(11, "RdBu")) +
  scale_size_manual(values = c(0.5, 1, 2)) +
  scale_colour_manual(values = color_pal(3)) +
  guides(size = guide_legend(title = "Mantel's r",
                             override.aes = list(colour = "grey35"), 
                             order = 2),
         colour = guide_legend(title = "Mantel's p", 
                               override.aes = list(size = 3), 
                               order = 1),
         fill = guide_colorbar(title = "Pearson's r", order = 3))
```

## pairs plot

```{r}
qpairs(iris) + geom_pairs()
```

## Citation

To cite linkET in publications use:

Houyun Huang(2021). linkET: Everything is Linkable. R package version 0.0.3.
